quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-07 paper-quollr.Rmd
small change to installation section now being availability
Removed all the notations

## Installation

The development version can be installed from GitHub:

```r
pak::pak("JayaniLakshika/quollr")
```

@@

`scurve` is a $7\text{-}D$ simulated dataset. It is constructed by simulating $1000$ observations from

@@

```{r notation-tb-html, eval=knitr::is_html_output()}
# Notation used in the paper

notation_df <- read_csv("misc/notation.csv")

notation_df |> 
  kable(caption = "Summary of notation for describing new methodology.") 
```

```{r notation-tb-pdf, eval=knitr::is_latex_output()}

notation_df <- read_csv("misc/notation.csv")

notation_df |> 
  kable(caption = "Summary of notation for describing new methodology.", booktabs = T) |>
  column_spec(1, width = "3cm") |>
  column_spec(2, width = "10cm") |>
  column_spec(3, width = "3cm")
```

>>>>

## Availability

The package is available on CRAN, and the development version is available at https://jayanilakshika.github.io/quollr/.

@@

The `scurve` is a $7\text{-}D$ simulated dataset. It is constructed by simulating $1000$ observations from

@@

### 2025-10-07 paper-quollr.tex
Rendered after Di's updates
Removed all the notations

\subsection{Installation}\label{installation}

The development version can be installed from GitHub:

\begin{verbatim}
pak::pak("JayaniLakshika/quollr")
\end{verbatim}

@@

\texttt{scurve} is a \(7\text{-}D\) simulated dataset. It is constructed by simulating \(1000\) observations from

@@

\begin{table}

\caption{\label{tab:notation-tb-pdf}Summary of notation for describing new methodology.}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{10cm}>{\raggedright\arraybackslash}p{3cm}}
\toprule
Notation & Description & Variable\\
\midrule
\textbackslash{}\$n, p, k\textbackslash{}\$ & number of observations, variables, embedding dimension, respectively & NA\\
\$\textbackslash{}mathbfit\{X\}, \textbackslash{}mathbfit\{x\}\$ & \$p\$-dimensional data (population, sample) & NA\\
\$\textbackslash{}mathbfit\{y\}\$ & \$k\$-dimensional layout & NA\\
\$P\$ & orthonormal basis, generating a \$d\textbackslash{}text\{-\}dimensional\$ linear projection of \$p\$-dimensional data & NA\\
\$T\$ & true  model & NA\\
\addlinespace
\$g\$ & functional mapping from \textbackslash{}pD\{\} to \textbackslash{}kD\{\}, especially as prescribed by NLDR & NA\\
\$\textbackslash{}mathbfit\{\textbackslash{}theta\}\$ & (Hyper-) parameters for NLDR method & NA\\
\$r\$ & ranges of the embedding components & NA\\
\$C\textasciicircum{}\{(j)\}\$ & \$j\$-dimensional bin centers & (c\_x, c\_y)\\
\$(b\_1, b\_2)\$ & number of bins in each direction & (b1, b2) = bins\\
\addlinespace
\$(a\_1, a\_2)\$ & binwidths, distance between centroids in each direction & a1, a2\\
\$(s\_1, \textbackslash{} s\_2)\$ & starting coordinates of the hexagonal grid & start\_point\\
\$q\$ & buffer to ensure hexgrid covers data, proportion of data range, 0-1 & q\\
\$m\$ & number of non-empty bins & m\\
\$b\$ & number of  hexagons in the grid & b\\
\addlinespace
\$h\$ & hexagonal id & NA\\
\$l\$ & side length & NA\\
\$A\$ & area & NA\\
\$n\_h\$ & bin count & NA\\
\$w\_h\$ & standardised bin counts & NA\\
\addlinespace
NA & threshold to extract high density hexagons & hd\_thresh\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\subsection{Availability}\label{availability}

The package is available on CRAN, and the development version is available at \url{https://jayanilakshika.github.io/quollr/}.

@@

The \texttt{scurve} is a \(7\text{-}D\) simulated dataset. It is constructed by simulating \(1000\) observations from

@@
